High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-05 paper/main.tex
finished summarizing key papers for discussion

\item \cite{SizeEtal18}:

\item \cite{ReimEtal17}

\item \cite{GonzEtal19}

\item \cite{BetzEtal19}

>>>>

\item \cite{SizeEtal18}: there are common patterns of connectivity
  (graph measures) across people; potential citation to motivate
  eigenvector centrality approach

\item \cite{ReimEtal17}: they propose that the brain processes stimuli
  by forming increasingly complex functional cliques and cavities;
  good motivation for our general approach

\item \cite{GonzEtal19}: dynamic functional connectivity during rest
  is influenced by spontaneous cognitive-task-like processes.  they
  also use low-dimensional embeddings to visualize how dynamic functional
  connectivity during rest can reveal periods of externally imposed tasks

\item \cite{BetzEtal19}: during movie watching, the brain's
  connectivity profile dynamically reconfigures.  when ISFC is high,
  this corresponds to times when network modularity is low and
  connectivity between cognitive systems is high.
